---
title: "Final Project"
author: "Liv Lindberg"
due date: "12/14/2020"
output: html_notebook
---


```{r}
# load packages
library(rvest)
library(tidyverse)
library(genius)
library(tidytext)
library(gridExtra)
data("stop_words")
data("sentiments")
```

```{r}
# read webpage for Grammy Awards
webpage <- read_html("https://en.wikipedia.org/wiki/Grammy_Award_for_Record_of_the_Year")

# copy xpath for table of 1980s
XPATH80 <- '/html/body/div[3]/div[3]/div[5]/div[1]/table[5]'

# run the following to create table of songs from 1980s
table_1980 <- 
  webpage %>%
  html_nodes(xpath = XPATH80) %>%
  html_table(fill = TRUE)

d1980 <- table_1980[[1]]
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

